Hannah Yu

### 2024-01-20 outputs/paper/paper.qmd
added new variable, started paper

---
title: "Hannah Yu"
subtitle: "My subtitle if needed"
author: 
  - First author
thanks: "Code and data are available at: LINK."
date: today
date-format: long
abstract: "First sentence. Second sentence. Third sentence. Fourth sentence."
format: pdf
number-sections: true
bibliography: references.bib
---

@@

library(tidyverse)
library(palmerpenguins)
```

@@

ggplot(penguins, aes(x = island, fill = species)) +
  geom_bar(alpha = 0.8) +
  scale_fill_manual(values = c("darkorange","purple","cyan4"),
                    guide = "none") +
  theme_minimal() +
  facet_wrap(~species, ncol = 1) +
  coord_flip()
```

>>>>

---
title: "Hannah Yu"
subtitle: "My subtitle if needed"
author: 
  - Hannah Yu
thanks: "Code and data are available at: ."
date: today
date-format: long
abstract: "First sentence. Second sentence. Third sentence. Fourth sentence."
format: pdf
number-sections: true
bibliography: references.bib
---

@@

#### Workspace set-up ####

## Load packages
library(tidyverse)
library(palmerpenguins)
library(ggplot2)

#read in cleaned data #
cleaned_homicide_data <- read.csv(here::here("inputs/data/cleaned_homicide_data.csv"))
show_col_types = FALSE
```

@@

ggplot(cleaned_homicide_data, aes(x = homicide_type)) +
  geom_bar(fill = "skyblue", color = "black") +
  labs(title = "Distribution of Homicide Types",
       x = "Homicide Types",
       y = "Count") +
  theme_minimal()

# ggplot(penguins, aes(x = island, fill = species)) +
#   geom_bar(alpha = 0.8) +
#   scale_fill_manual(values = c("darkorange","purple","cyan4"),
#                     guide = "none") +
#   theme_minimal() +
#   facet_wrap(~species, ncol = 1) +
#   coord_flip()
```

```{r}
ggplot(cleaned_homicide_data, aes(x = occurrence_year, y = count, group = 1)) +
  geom_line(color = "blue") +
  geom_point(color = "blue") +
  labs(title = "Homicide Occurrences Over the Years",
       x = "Year",
       y = "Number of Homicides") +
  theme_minimal()
```
